---
title: "Homework 1"
output: github_document
---

```{r}
library(tidyverse)
```

# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

In the `penguins` dataset, there are `r nrow(penguins)` rows and `r ncol(penguins)` columns. Columns include:

1. Species

2. Island

3. Bill Length (mm)

4. Bill depth (mm)

5. Flipper length (mm)

6. Body mass (g)

7. Sex

8. Year

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

Here is a scatterplot of bill length (mm) as the x-axis and flipper length (mm) as the y-axis.

```{r}
ggplot(
  penguins, 
  aes(x = bill_length_mm,
      y = flipper_length_mm,
      color = species)
  ) + geom_point()
```

```{r}
ggsave("penguins_scatterplot.png")
```

# Problem 2

```{r}
problem2_df =
  tibble(
    norm_samp = rnorm(10),
    log_vec = norm_samp > 0,
    char_vec = c("My", "Name", "Is", "Tiffany", "And", "This", "Is", "For", "Problem", "Two"),
    fac_vec = factor(c("Low", "Medium", "High", "Low", "Medium", "High", "Low", "Medium", "High", "Low"))
  )
```

The mean of `norm_samp` is `r mean(pull(problem2_df, norm_samp))`.

The mean of `log_vec` is `r mean(pull(problem2_df, log_vec))`.

The mean of `char_vec` is `r mean(pull(problem2_df, char_vec))`.

The mean of `fac_vec` is `r mean(pull(problem2_df, fac_vec))`.

I can take the mean of `norm_samp` and `log_vec`, but not `char_vec` and `fac_vec` because R cannot translate those vectors into numeric values.

```{r, results = "hide"}
as.numeric(pull(problem2_df, log_vec))

as.numeric(pull(problem2_df, char_vec))

as.numeric(pull(problem2_df, fac_vec))
```

R was able to convert `log_vec` and `fac_vec` into numeric values, but not `char_vec`. R mapped `TRUE` and `FALSE` values to `1` and `0` for `log_vec`, and mapped each factor level to its underlying integer for `fac_vec`. For `char_vec`, R was unable to translate strings into numeric values.
